#Git commands are not working on the console, we have to put them in the Terminal window

Preparation code for the shell terminal : 
git init
git branch -M main
#git rehub link : https://github.com/VaninaHeinrich/PTED_week-3.git
git remote add origin https://github.com/VaninaHeinrich/PTED_week-3.git
git push --set-upstream origin main

#Controle the projet options - Git to be sure the rehub link was added
#as the push option was not working, I recreate the projet and connected it to the git repo the same way as week 2

```{r}
library(readr)        # to import tabular data (e.g. csv)
library(dplyr)        # to manipulate (tabular) data
library(ggplot2)      # to visualize data
library(sf)           # to handle spatial vector data
library(terra)        # To handle raster data
library(lubridate)    # To handle dates and times
```


Task 1 ---------------------------------

Import the data 

```{r}
library(readr)
caro60 <- read_csv("caro60.csv", col_types = cols(CollarID = col_number(), DatetimeUTC = col_datetime(format = "%Y-%m-%dT%H:%M:%SZ")))
View(caro60)
```

```{r}
caro_6 <- slice(caro60, seq(from = 1, to = 200, by = 6))
```

