#Git commands are not working on the console, we have to put them in the Terminal window

Preparation code for the shell terminal : 
git init
git branch -M main
#git rehub link : https://github.com/VaninaHeinrich/PTED_week-3.git
git remote add origin https://github.com/VaninaHeinrich/PTED_week-3.git
git push --set-upstream origin main

#Controle the projet options - Git to be sure the rehub link was added
#as the push option was not working, I recreate the projet and connected it to the git repo the same way as week 2

```{r}
library(readr)        # to import tabular data (e.g. csv)
library(dplyr)        # to manipulate (tabular) data
library(ggplot2)      # to visualize data
library(sf)           # to handle spatial vector data
library(terra)        # To handle raster data
library(lubridate)    # To handle dates and times
```


Task 1 ---------------------------------

Import the data 

```{r}
library(readr)
caro60 <- read_csv("caro60.csv", col_types = cols(CollarID = col_number(), DatetimeUTC = col_datetime(format = "%Y-%m-%dT%H:%M:%SZ")))
View(caro60)
```

Window interval of 6 minutes (n +/- 3)

```{r}
caro <- mutate(caro60, nMinus3 = sqrt((lag(E,3)-E)^2+(lag(N,3)-N)^2), nMinus2 = sqrt((lag(E,2)-E)^2+(lag(N,2)-N)^2), nMinus1 = sqrt((lag(E,1)-E)^2+(lag(N,1)-N)^2), nPlus1  = sqrt((E-lead(E,1))^2+(N-lead(N,1))^2), nPlus2  = sqrt((E-lead(E,2))^2+(N-lead(N,2))^2), nPlus3  = sqrt((E-lead(E,3))^2+(N-lead(N,3))^2))

View(caro)
```

Task 2 ----------------------------------

```{r}
caro <- caro %>% rowwise() %>% mutate(stepMean = mean(c(nMinus3, nMinus2, nMinus1,nPlus1,nPlus2, nPlus3))) %>%ungroup() 

View(caro)
```

Explore the data to find a acceptable threshold to differentiate moves and stops

```{r}
summary(caro)
```

mean of stepmean is :  6.951, I decide to take this mean as my threshold.

Remove static points

1st step : defining if the animal is moving or not (static = false means moving, static = true means stop)

```{r}
caro <- caro %>% ungroup() %>% mutate(static = stepMean < mean(stepMean, na.rm = TRUE))
View(caro)
```


Task 3 -------------------------------------------------------------------------

```{r}
caro %>%ggplot(aes(E, N))  + geom_path(color = "gray") + geom_point(aes(color = static)) + coord_fixed() + theme(legend.position = "right")
```

Task 4 -------------------------------------------------------------------------

```{r}
rle_id <- function(vec){
  x <- rle(vec)$lengths
  as.factor(rep(seq_along(x), times=x))
  }
```

```{r}
caro <- mutate(caro, segment_id = rle_id(static))
caro
```
```{r}
caro_filter <- caro %>% filter(!static)
View(caro_filter)
```

```{r}
caro1 <- caro_filter %>%ggplot(aes(E, N))  + geom_path(color = caro_filter$segment_id) + geom_point(color = caro_filter$segment_id) + coord_fixed() + theme(legend.position = "right") + ggtitle("All segments (uncleaned)")
caro1
```
```{r}
#install.packages("plyr")
library(plyr)
ddply(caro_filter, .(segment_id), nrow)
```
The result show that segment_id 10 and 12 have less then 5 minutes segments. 
Removing segment_id 10 and 12

```{r}
caro_filter2 <- caro_filter[!(caro_filter$segment_id=="10" | caro_filter$segment_id=="12"),]
View(caro_filter2)
```

```{r}
caro2 <- caro_filter2 %>%ggplot(aes(E, N))  + geom_path(color = caro_filter2$segment_id) + geom_point(color = caro_filter2$segment_id) + coord_fixed() + theme(legend.position = "right") + ggtitle("Long segments (removed seg < 5)")
caro2
```

showing both graphs next to each other : 

```{r}
grid.arrange(caro1, caro2, ncol=2, nrow=1, top = "Moving segments coloured by Segment ID")
```

Task 5 ------------------------------------------------------------------------

```{r}
library(readr)
pedestrian <- read_csv("pedestrian.csv", 
    col_types = cols(TrajID = col_number(), 
        E = col_number(), N = col_number(), 
        DatetimeUTC = col_datetime(format = "%Y-%m-%dT%H:%M:%SZ")))
View(pedestrian)
```

How many pedestrian do we have ? 
```{r}
library(plyr)
ddply(pedestrian, .(TrajID), nrow)
```
we have 6 pedestrians, we need 6 subsets to make 6 graphs

```{r}
P1 <- subset(pedestrian, TrajID == "1")
P2 <- subset(pedestrian, TrajID == "2")
P3 <- subset(pedestrian, TrajID == "3")
P4 <- subset(pedestrian, TrajID == "4")
P5 <- subset(pedestrian, TrajID == "5")
P6 <- subset(pedestrian, TrajID == "6")
```

to verify if the subset function did work, i can just view them and see if the tibble has the same number of rows as the ddply function showed

```{r}
G1 <- ggplot(P1, aes(E,N)) + geom_point(colour = "red") + geom_path(colour = "red") + ggtitle("TrajID 1") + theme(legend.position="none", plot.title = element_text(hjust = 0.5))
G2 <- ggplot(P1, aes(E,N)) + geom_point(colour = "blue") + geom_path(colour = "blue") + ggtitle("TrajID 2") + theme(legend.position="none", plot.title = element_text(hjust = 0.5))
G3 <- ggplot(P3, aes(E,N)) + geom_point(colour = "orange") + geom_path(colour = "orange") + ggtitle("TrajID 3") + theme(legend.position="none", plot.title = element_text(hjust = 0.5))
G4 <- ggplot(P4, aes(E,N)) + geom_point(colour = "yellow") + geom_path(colour = "yellow") + ggtitle("TrajID 4") + theme(legend.position="none", plot.title = element_text(hjust = 0.5))
G5 <- ggplot(P5, aes(E,N)) + geom_point(colour = "gray") + geom_path(colour = "gray") + ggtitle("TrajID 5") + theme(legend.position="none", plot.title = element_text(hjust = 0.5))
G6 <- ggplot(P6, aes(E,N)) + geom_point(colour = "green") + geom_path(colour = "green") + ggtitle("TrajID 6") + theme(legend.position="none", plot.title = element_text(hjust = 0.5))
grid.arrange(G1, G2, G3, G4, G5, G6, top = "Visual comparison of the 6 trajectories")
```


