#Git commands are not working on the console, we have to put them in the Terminal window

Preparation code for the shell terminal : 
git init
git branch -M main
#git rehub link : https://github.com/VaninaHeinrich/PTED_week-3.git
git remote add origin https://github.com/VaninaHeinrich/PTED_week-3.git
git push --set-upstream origin main

#Controle the projet options - Git to be sure the rehub link was added
#as the push option was not working, I recreate the projet and connected it to the git repo the same way as week 2

```{r}
library(readr)        # to import tabular data (e.g. csv)
library(dplyr)        # to manipulate (tabular) data
library(ggplot2)      # to visualize data
library(sf)           # to handle spatial vector data
library(terra)        # To handle raster data
library(lubridate)    # To handle dates and times
```


Task 1 ---------------------------------

Import the data 

```{r}
library(readr)
caro60 <- read_csv("caro60.csv", col_types = cols(CollarID = col_number(), DatetimeUTC = col_datetime(format = "%Y-%m-%dT%H:%M:%SZ")))
View(caro60)
```

Window interval of 6 minutes (n +/- 3)

```{r}
caro <- mutate(caro60, nMinus3 = sqrt((lag(E,3)-E)^2+(lag(N,3)-N)^2), nMinus2 = sqrt((lag(E,2)-E)^2+(lag(N,2)-N)^2), nMinus1 = sqrt((lag(E,1)-E)^2+(lag(N,1)-N)^2), nPlus1  = sqrt((E-lead(E,1))^2+(N-lead(N,1))^2), nPlus2  = sqrt((E-lead(E,2))^2+(N-lead(N,2))^2), nPlus3  = sqrt((E-lead(E,3))^2+(N-lead(N,3))^2))

View(caro)
```

Task 2 ----------------------------------

